\selectlanguage{english}
\begin{abstract}
    
The use of relational databases and database normalization problems have been a field of interest to many computer scientists over the decades. There have been many solutions to these problems over the years, but there are still gaps in some aspects. As a teaching assistant at the Faculty of Technical Sciences in Novi Sad, we were thinking about developing a program that would be a proper tool for performing teaching assistant tasks. Our main requirement is that the software need to support the normalization algorithms studied at the university: the synthesis and decomposition algorithms. A requirement for the decomposition algorithm is to implement an interactive flow of the algorithm. An additional detail of the requirements was that task series need to be easily specified and replaced.

As a result of these requirements, we developed an application called \textit{RelNorm} to solve the problem of normalizing relational databases as a console application. It is an application written in the \textit{Java} programming language that breaks down a relational schema into multiple relational schemas, depending on the normalization algorithm. Unit tests were used to verify the correctness of the implementation. Code base analysis was done with \textit{SonarCloud} measuring code coverage, reliability and maintainability. The results of the tests and the analysis are included in this paper.

\textit{RelNorm} has already been proven in practice, as it has already been used by teaching assistants in the 2021/2022 academic year to assemble database normalization task series and review solved tasks.

Keywords: relational database, normalization, relational schemas, software testing, code coverage.

\end{abstract}